Hyperopt-Sklearn: Subtitle?

### 2014-04-26 papers/2014-automl/paper.tex
add newsgroup numbers and sklearn search diagram

\begin{table}
    \caption{
        Hyperopt-sklearn scores relative to selections from literature on the three data sets used in our experiments.
        On MNIST, hyperopt-sklearn is one of the best-scoring methods that does not use image-specific domain knowledge (these scores and others may be found at http://yann.lecun.com/exdb/mnist/).
        On 20 Newsgroups, XXX.
        On Convex Images, hyperopt-sklearn outperforms previous automatic algorithm configuration approaches~\citep{eggensperger+etal:2013} and manual tuning~\citep{larochelle+etal:2007}.
    }
    \label{tbl:acc}
    \centering
    \small
    \begin{tabular}{llllll}
        \hline
        \multicolumn{2}{c}{\textbf{MNIST}} & \multicolumn{2}{c}{\textbf{20 Newsgroups}} & \multicolumn{2}{c}{\textbf{Convex Images}}  \\
        Approach & Accuracy  & Approach & Accuracy & Approach & Accuracy\\
        \hline
        Committee of convnets & 99.8\%                & thing & 85\%  & \textbf{hyperopt-sklearn} & 88.9\%\\
        \textbf{hyperopt-sklearn} & \textbf{98.7}\%   & thing & 85\%  & hp-dbnet & 84.6\% \\
        libSVM grid search & 98.6\%                   & thing & 85\% & dbn-3 & 81.4\%\\
        Boosted trees & 98.5\%                        & thing & 85\%  &  &  \\
    \end{tabular}
\end{table}

@@

\begin{figure}
    \centering
    \includegraphics[width=2.90in]{graphics/AverageTestScoresClassifiersTPE}
    \caption{
        For each data set, searching the full configuration space (``Any Classifier'') delivered performance approximately on par with a search that was restricted to the best classifier type.
        (Best viewed in color.)
    }
    \label{fig:avg_test_scores}
%\vspace{-3em}
\end{figure}

>>>>

\begin{table}
    \caption{
        Hyperopt-sklearn scores relative to selections from literature on the three data sets used in our experiments.
        On MNIST, hyperopt-sklearn is one of the best-scoring methods that does not use image-specific domain knowledge (these scores and others may be found at http://yann.lecun.com/exdb/mnist/).
        On 20 Newsgroups, XXX.
        On Convex Images, hyperopt-sklearn outperforms previous automatic algorithm configuration approaches~\citep{eggensperger+etal:2013} and manual tuning~\citep{larochelle+etal:2007}.
    }
    \label{tbl:acc}
    \centering
    \small
    \begin{tabular}{llllll}
        \hline
        \multicolumn{2}{c}{\textbf{MNIST}} & \multicolumn{2}{c}{\textbf{20 Newsgroups}} & \multicolumn{2}{c}{\textbf{Convex Images}}  \\
        Approach & Accuracy  & Approach & F-Score & Approach & Accuracy\\
        \hline
        Committee of convnets & 99.8\%                & CFC & .928 & \textbf{hyperopt-sklearn} & 88.7\%\\
	\textbf{hyperopt-sklearn} & \textbf{98.7}\%   & hyperopt-sklearn & \textbf{.856} & hp-dbnet & 84.6\% \\
        libSVM grid search & 98.6\%                   & SVMTorch & .848 & dbn-3 & 81.4\%\\
        Boosted trees & 98.5\%                        & LibSVM & .843 &  &  \\
    \end{tabular}
\end{table}

@@

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{graphics/sklearn_space_all_together}
    \caption{
	    XXX
    }
    \label{fig:space}
\end{figure}
\begin{figure}
    \centering
    \includegraphics[width=2.90in]{graphics/AverageTestScoresClassifiersTPE}
    \caption{
        For each data set, searching the full configuration space (``Any Classifier'') delivered performance approximately on par with a search that was restricted to the best classifier type.
        (Best viewed in color.)
    }
    \label{fig:avg_test_scores}
%\vspace{-3em}
\end{figure}
